A quantum parallel Markov chain Monte Carlo

### 2022-03-03 main.tex
finished dicussion

We have shown how parallel MCMC may enjoy quadratic speedups by combining quantum minimization with the Gumbel-max trick.  Within a QPMCMC iteration, the current state represents a warm-start for the sampling-turned-optimization problem, leading to increased efficiencies for the quantum minimization algorithm.  This work leads to two immediate questions.  First, more recent quantum minimization algorithms exist \citep{baritompa2005grover,farhi2014quantum}.  Would these confer additional speedups for quantum parallel MCMC and benefit from warm-starting in a similar manner? Second, there are other algorithms in statistics and machine learning that require sampling from potentially costly discrete distributions \citep{liu2001theoretical,csillery2010approximate}.  Can one adapt  the proposed strategies to these?  Large-scale, practical quantum computing is still a long way off, but quantum algorithms are ripe for conventional computational statistics.

>>>>

We have shown how parallel MCMC may enjoy quadratic speedups by combining quantum minimization with the Gumbel-max trick.  Within a QPMCMC iteration, the current state represents a warm-start for the sampling-turned-optimization problem, leading to increased efficiencies for the quantum minimization algorithm.  This work leads to two immediate questions.  First, more recent quantum minimization algorithms exist \citep{baritompa2005grover,farhi2014quantum}.  Would these confer additional speedups for quantum parallel MCMC and benefit from warm-starting in a similar manner? Second, there are other models and algorithms in statistics, machine learning and statistical mechanics that require sampling from potentially costly discrete distributions.  Can one adapt  the proposed strategies to these?  Large-scale, practical quantum computing is still a long way off, but quantum algorithms are ripe for mainstream computational statistics.
